### 2022-11-21 ms.rmd
Update on rerun

# Intercept only model. 
rerun = FALSE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                              random = list(~1 | record_num,
                                              ~1 | species_full,
                                              ~1 | spp,
                                              ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}

>>>>

# Intercept only model. 
rerun = TRUE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ c_accl_time + type, V = V, 
                              random = list(~1 | record_num,
                                              ~1 | species_full,
                                              ~1 | spp,
                                              ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}
